Title

### 2018-07-31 thesis/paper/paper.tex
Moved text to correct section

\subsection{Distinct values (Q21502410)}
The distinct values constraint forbids the existence of two constrained statements with the same value.
\begin{table}[H]
\caption{distinct values constraint (Q21502410)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & constrained statement value \\
\hline
Violations & two constrained statements with same value \\
\hline
Dependency & all constrained statements\\
\hline
Rule features & inequality \\
\hline
\end{tabularx}
\end{table}
To model the distinct values constraint it is necessary to find triples tripleEDB with the constrained property and the same value whose statement id is unequal.

@@

Modelling the constraint requires a predicate associating the value or the statement with its unit and inequality between every unit and all allowed units. Then a violation can be found by finding all tripleEDB with the constrained property and a unit unequal to all allowed units. In theory the constraint can also be applied to qualifiers and references by setting the respective value on a constraint scope (P4680) qualifier. However, there is currently no such case and will therefore not be regarded.

@@

The violations can then be found using the same premises with inequality added.
\todo[inline]{Kind of ridiculous to write basically the same premise repeatedly. Should probably write the general approach in demand-driven and just write the normal inequality here}

>>>>

\subsection{Distinct values (Q21502410)}
The distinct values constraint forbids the existence of two constrained statements with the same value.
\begin{table}[H]
\caption{distinct values constraint (Q21502410)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & constrained statement value \\
\hline
Violations & two constrained statements with same value \\
\hline
Dependency & all constrained statements\\
\hline
Rule features & inequality \\
\hline
\end{tabularx}
\end{table}
To model the distinct values constraint it is necessary to find triples tripleEDB with the constrained property and the same value whose statement id is unequal. In theory the constraint can also be applied to qualifiers and references by setting the respective value on a constraint scope (P4680) qualifier. However, there is currently no such case and will therefore not be regarded.

@@

Modelling the constraint requires a predicate associating the value or the statement with its unit and inequality between every unit and all allowed units. Then a violation can be found by finding all tripleEDB, qualifierEDB and referenceEDB with the constrained property and a unit unequal to all allowed units. Theoretically some of these can be excluded by using the constraint scope (P4680) qualifier on the constraint but there is no current case where this is done.

@@

The violations can then be found using the same premises with inequality added.
